Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-04-18 docs/00-manuscripts/ieee/ieee-manuscript.tex
correct permutation execution

% FIXME Talk about the bias of permutation FI in highly correlated settings
\noindent Estimating feature importance for highly-correlated datasets is a complicated task.
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features.
Methods like \ac{PDP} do not produce reliable estimates in such scenarios because unrealistic combinations between covariates are created \cite{molnar2019}.
% FIXME: Add ref
Due to the noisiness of the dataset, estimates from model-agnostic approaches such as permutation-based feature importance should also be taken with care.
This method calculates the loss of predictive performance for each feature by permuting it in a random manner.
The more important the feature is for the model, the higher the mean loss in the measure, reflecting the importance of the specific feature for the current model.
Fitting many models on the dataset containing the permuted feature comes with some computational cost.
For increased efficiency, we estimated the feature importance only for datasets HR and VI using the best performing learner of the benchmark.

@@

\noindent The decision to use a buffer of 2 m to generate the index value for each observation has to be seen critical.
Due to the reported geometric offset of up to 1 m for the hyperspectral data, the possibility of assigning a wrong pixel value to a tree observation would be high.
Using a buffer of more than 2 meters increases the probability of including information from other trees into the pixel value, blurring the actual value of the tree observation.
In our view using a buffer of 2 m is a good compromise between including information of too many surrounding trees and not accounting for the geometric offset.
In addition, a side-analysis showed that some trees would be assigned missing values when relying on a single pixel.
This then would result in the removal of that particular tree which we wanted to avoid.
Even though we provide no results showing the influence of multiple buffer values on the extraction, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.

>>>>

% FIXME Talk about the bias of permutation FI in highly correlated settings
\noindent Estimating feature importance for highly-correlated datasets is a complicated task.
The correlation between covariates makes it challenging to calculate an unbiased estimate for single features.
Methods like \ac{PDP} do not produce reliable estimates in such scenarios because unrealistic combinations between covariates are created \cite{molnar2019}.
% FIXME: Add ref
Due to the noisiness of the dataset, estimates from model-agnostic approaches such as permutation-based feature importance should also be taken with care.
This method calculates the loss of predictive performance for each feature by permuting it in a random manner.
The more important the feature is for the model, the higher the mean loss in the measure, reflecting the importance of the specific feature for the current model.
Predicting and calculating the error measure multiple times per feature comes with some computational cost.
For increased efficiency, we estimated the feature importance only for datasets HR and VI using the best performing learner of the benchmark.

@@

\noindent The decision to use a buffer of 2 m to generate the index value for each observation has to be seen critical.
Due to the reported geometric offset of up to 1 m for the hyperspectral data, the possibility of assigning a wrong pixel value to a tree observation would be high.
Using a buffer of more than 2 meters increases the probability of including information from other trees into the pixel value, blurring the actual value of the tree observation.
In our view using a buffer of 2 m is a good compromise between including information of too many surrounding trees and not accounting for the geometric offset.
Even though we provide no results showing the influence of multiple buffer values on the extraction, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.
